Tables

### 2020-09-21 tables.Rmd
misc

```{r table4-regression-models-muscle-thickness}
# Save model 
hyp.pre.m1 <- readRDS( "./data/derivedData/ubf-tot-rna-model/hyp_pre_m1.RDS")
hyp.pre.m2 <- readRDS( "./data/derivedData/ubf-tot-rna-model/hyp_pre_m2.RDS")
hyp.pre.m3 <- readRDS( "./data/derivedData/ubf-tot-rna-model/hyp_pre_m3.RDS")

m1.sum <- summary(hyp.pre.m1)
m2.sum <- summary(hyp.pre.m2)
m3.sum <- summary(hyp.pre.m3)

@@

  flextable() %>%
  set_header_labels(coef = "Coefficient", 
                    Est.Error = "SD", 
                    lwr = "Lower 95% CI", 
                    upr = "Upper 95% CI") %>%
    add_header_lines(values = "Table 3. Total RNA as a predictor of muscle growth.") %>%

>>>>

```{r table3-regression-models-muscle-thickness}
# Save model

comb.m1 <- readRDS("./data/derivedData/ubf-tot-rna-model/comb_m1.RDS")

comb.m1 <- summary(comb.m1)

reg_results <- 
  cbind(rbind(comb.m1$fixed,
      comb.m1$random$participant, 
      comb.m1$random$`participant:leg`, 
      comb.m1$spec_pars), 
      data.frame(coef = c("Intercept", 
                          "UBF protein levels (SD-units)", 
                          "Session 1-4",
                          "Session 4-8", 
                          "Session 8-12", 
                          "De-training",
                          "Between Participant variation",
                          "Between Participant:Leg variation", 
                          "Residual SD"))) %>%
  remove_rownames() %>%
  dplyr::select(coef, Estimate, Est.Error, lwr = `l-95% CI`, upr = `u-95% CI`)

  flextable() %>%
  set_header_labels(coef = "Coefficient", 
                    Est.Error = "SD", 
                    lwr = "Lower 95% CI", 
                    upr = "Upper 95% CI") %>%
    add_header_lines(values = "Table 3. Effect of UBF levels, sessions and de-training on RNA-levels.") %>%

 # hline(i = c(9, 17), part="body", border = std_border ) %>%
      fontsize(size = 8, part = "body") %>%
    fontsize(size = 10, part = "header") %>%
      fontsize(size = 7, part = "footer") %>%

  footnote( i = 2, j = 2,
            value = as_paragraph(
              c("The dependent variable is total RNA levels (log)")
            ),
            ref_symbols = c("a"),
            part = "header", inline = TRUE) %>%
    footnote( i = c(3, 4, 5), j = 1,
            value = as_paragraph(
              c("Slope in response to session 1-4", 
                "Change in slope in session 4-8", 
                "Change in slope in session 8-12")
            ),
            ref_symbols = c("b","c","d"),
            part = "body", inline = TRUE) %>%

```{r table4-regression-models-muscle-thickness}
# Save model

hyp.pre.m3 <- readRDS( "./data/derivedData/ubf-tot-rna-model/hyp_pre_m3.RDS")

m3.sum <- summary(hyp.pre.m3)

@@

  flextable() %>%
  set_header_labels(coef = "Coefficient", 
                    Est.Error = "SD", 
                    lwr = "Lower 95% CI", 
                    upr = "Upper 95% CI") %>%
    add_header_lines(values = "Table 4. Total RNA as a predictor of muscle growth.") %>%
